\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-08 papers/itsc_2012/draft2.tex
gridlock diagram
2 more citations and scale

The default behavior maximizes acceleration while obeying speed limits,
avoiding collisions, and obeying intersections. By considering the highest speed
achievable at the end of the next step and the subsequent stopping distance at
this speed, the behavior can scan sufficiently far ahead along several
traversables to locate agents to avoid and intersections to query. The analysis
short-circuits at the first nearby agent and intersection requiring a stop,
since it would be illegal to drive further anyway.

@@

@@

\subsection{Determinism and other simulation properties}

@@

\commentd{give some informal or formal (with numbers) idea of scale / how many
agents we can simulate in different map sizes} \commentpk{I would say that the the last point is fairly important}

\commentd{http://sumo.sourceforge.net/pdf/mieec1.pdf gives their measure as
  agent updates / second. This is indep of dt and num of agents, assuming
  nothing grows nonlinearly with more agents. our initial result on my box is
  about 150,000 moves / second. so with 500 agents, runs 30x faster than
  reality. with 5,000, runs about 3x faster. with 50,000 (yes, this works!),
  runs at 1/3 the speed of reality (it takes 1 real second to simulate 0.3
  seconds)}
\commentm{I typically have 160k-170k agent steps per second on my machine.  The
	highest I have seen is upwards of 300k, but that was because most agents had
	gridlocked...}

@@

AORTA's map construction process, although flexible, is fraught with heuristics,
motivating proposed changes to OSM. Road type annotations imprecisely estimate
the number of lanes and typical speed limits, resulting in incorrect graphs.
Guessing the turns at each intersection makes common road features like right
turn-only lanes and shared center left turn lanes hard to detect. There are many
circumstances where AORTA simulates one intersection as several in close
proximity because roads do not geometrically line up, but semantically they do.
If OSM could encode this, the performance of intersection policies such as
traffic signals would vastly improve in those regions.

>>>>

The default behavior maximizes acceleration while obeying speed limits,
avoiding collisions, and obeying intersections. By considering the highest speed
achievable at the end of the next step and the subsequent stopping distance at
this speed, the behavior's lookahead engine can scan sufficiently far ahead
along several traversables to locate agents to avoid and intersections to query.
The analysis short-circuits at the first nearby agent and intersection requiring
a stop, since it would be illegal to drive further anyway.

@@

\pix{gridlock.png}{Each of the red agents wants to turn left, so none of them
can. The traffic jam will slowly build up around this intersection.}{scale=0.25}

@@

\subsection{Determinism and scale}

@@

The speed of simulation depends on the step duration $dt$, the map size, and the
number of agents. A measure independent of these factors is the number of agent
steps per second. On a $2.4$ GHz machine, this can be observed to average at
about $150,000$, a number comparable to existing simulators \cite{SUMOthesis}.
Further optimizations are planned.

@@

AORTA's map construction process, although flexible, is fraught with heuristics,
motivating proposed changes to OSM. Road type annotations imprecisely estimate
the number of lanes and typical speed limits, resulting in incorrect graphs.
Guessing the turns at each intersection makes common road features like right
turn-only lanes and shared center left turn lanes hard to detect. There are many
circumstances where AORTA simulates one intersection as several in close
proximity because roads do not geometrically line up, but semantically they do.
If OSM could encode this, the performance of intersection policies such as
traffic signals would vastly improve in those regions. Other simulators have
identified similar issues before \cite{Krajzewicz_Hertkorn_Ringel_Wagner_2005}.
